Clustering Beat-Chroma Patterns in a Large Music Database

### 2010-03-23 Paper/Paper.tex
intro to experiemnts section shorten

\begin{algorithm}
%\caption{Pseudocode of Vector Quantization}
\begin{algorithmic}
\STATE$l$ learning rate
\STATE$\{P_n\}$ set of patches
\STATE$\{C_k\}$ codebook of $K$ codes
%\STATE $m \leftarrow b$
\REQUIRE $0 < l \leq 1$
\FOR{$nIters$}
\FOR{$p \in \{P_n\}$}
\STATE$c \leftarrow min_{c \in C_k} dist(p,c)$
\STATE$c \leftarrow c + (p - c) * l$
\ENDFOR
\ENDFOR
\RETURN $\{C_k\}$
\caption{\small{Pseudocode of Online Vector Quantization. Note that we can 
replace the number of iteration by a threshold on the distortion over some 
test set.}
\label{algo:vq}}
\end{algorithmic}
\end{algorithm}

\section{Experiments}\label{sec:experiments}
In this section we assert the basic properties of our encoding scheme.
The first subsection gives the details to reproduce the experiments,
such as the distance measure and learning rate. In the second subsection, we
measure properties such as ``how the number of codes affect the distortion''
and ``how many learning samples should we use''. Though important numbers
to report, the busy reader could skip to subsection \ref{ssec:random}
and the following sections.
Note that we will present two additional experiments in 
Section \ref{sec:exps2}.

>>>>

\begin{algorithm}
%\caption{Pseudocode of Vector Quantization}
\begin{algorithmic}
\STATE$l$ learning rate
\STATE$\{P_n\}$ set of patches
\STATE$\{C_k\}$ codebook of $K$ codes
%\STATE $m \leftarrow b$
\REQUIRE $0 < l \leq 1$
\FOR{$nIters$}
\FOR{$p \in \{P_n\}$}
\STATE$c \leftarrow min_{c \in C_k} dist(p,c)$
\STATE$c \leftarrow c + (p - c) * l$
\ENDFOR
\ENDFOR
\RETURN $\{C_k\}$
\caption{\small{Pseudocode of Online Vector Quantization. Note that we can 
replace the number of iterations by a threshold on the distortion over some 
test set.}
\label{algo:vq}}
\end{algorithmic}
\end{algorithm}

\section{Experiments}\label{sec:experiments}
In this section we present different clustering experiments. We introduce
our training data and our main testing data. Some detailed settings
of our algorithm are also provided. Then, we answer some common questions
about any clustering algorithms, for instance 
``how the number of codes affect the distortion''
and ``how many learning samples should we use''.
Note that we will present two additional experiments in 
Section \ref{sec:exps2}.
